Calculating life expectancy and exploring missingness

### 2017-04-06 Code/1_Explore_Data.Rmd
add RID and partition data

head(dat)
```

@@

```{r write_data_to_csvs}
#save.image(file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/Sep6_BWgap.Rdata")
write_csv(dat.clean, path = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_clean.csv", col_names = T)
write_csv(dat.aggregated, path = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_aggregated.csv", col_names = T)
```

>>>>

head(dat)

dat$stabbrs <- state.abb[match(dat$state, state.name)]
unique(dat$state[is.na(dat$stabbrs)==T]) #Washington DC not defined

dat$stabbrs[dat$state == "Washington DC"] <- "DC"

dat$stabbrs <- factor(dat$stabbrs)

dat$RID <- paste(dat$stabbrs, dat$year, substr(dat$sex, 1, 1),
                 substr(dat$race, 1, 1), dat$age.n, dat$COD, sep = ".")
```

@@

```{r write_data_to_csvs}
#save.image(file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/Sep6_BWgap.Rdata")
write_csv(dat.clean, path = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_clean.csv", col_names = T)
write_csv(dat.aggregated, path = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_aggregated.csv", col_names = T)

excluded.states <- c("Alaska", "Hawaii", "Idaho", "Maine", "Montana", 
                     "New Hampshire", "North Dakota", "South Dakota", "Utah", "Vermont", "Wyoming")

included.states <- setdiff(unique(levels(dat.clean$state)), excluded.states)

for(i in 1:length(included.states)) { 
  name = paste0('dat_clean_', included.states[i], '.csv')
  ds_temp = dat.clean[dat.clean$state == included.states[i], ]
  write.csv(ds_temp, file=name)
}
rm(ds_temp)
```
